---
output:
  bookdown::html_document2:
    fig_cap: TRUE
    df_print: paged
    number_sections: FALSE
    toc: yes
    toc_depth: 4
    toc_collapsed: yes
    toc_float: yes
params:
    set_title: "NDQ Issue Review (version)"
title: "`r params$set_title`"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)
require(plotly)
require(RColorBrewer)
require(argos)
require(srcr)
require(tidyverse)
require(ggiraph)
library(gt)
library(forcats)
library(fontawesome)
source('../code/cohort_colors.R')
site <- 'dcc'
ndq_session<-argos$new('ndq_session')$init_session(
  db_src = Sys.getenv('PEDSNET_DB_SRC_CONFIG_BASE'),
  cdm_schema = paste0(site, '_pedsnet'), 
  results_schema = 'dqa_rox', 
  retain_intermediates = FALSE,
  db_trace = FALSE, 
  results_name_tag = ''
)

prev_session<-argos$new('ndq_session_prev')$init_session(
  db_src = Sys.getenv('PEDSNET_DB_SRC_CONFIG_BASE_PREV'), 
  cdm_schema = paste0(site, '_pedsnet'), 
  results_schema = 'dqa_rox',
  retain_intermediates = FALSE,
  db_trace = FALSE,
  results_name_tag = ''
)

set_argos_default(ndq_session)
```

```{r table_setup}
sitenames<-results_tbl('thresholds_history')%>%filter(site!='default')%>%distinct(site)%>%arrange(site)%>%pull()
metadata<-results_tbl('dqa_check_metadata')%>%
  collect()
 
viol<-results_tbl('threshold_tbl_violations')%>%
  collect()%>%
  left_join(metadata, by='check_name')%>%
  mutate(value_output=round(value_output,2))

viol_prev_ct<-prev_session$results_tbl('threshold_tbl_violations')%>%
  group_by(site)%>%
  summarise(n_prev=n())%>%
  collect()
n_viol_by_checktype<-metadata%>%
  left_join(viol,by=c('check_name','check_type'))%>%
  group_by(check_type)%>%
  summarise(n_sites=case_when(all(is.na(site))~0,
                              TRUE~n_distinct(site)-1),
            n_issues=sum(violation, na.rm=TRUE))%>%
  ungroup()
n_viol_bycheck<-viol%>%
  group_by(check_type)%>%
  mutate(num_total=n_distinct(site))%>%
  ungroup()%>%
  group_by(check_type,check_name_app, num_total)%>%
  summarise(n_sites=n_distinct(site))%>%
  ungroup()%>%
  mutate(check_type=paste0(check_type, " (", num_total, " total sites)"))%>%
  select(-num_total)
```

# Purpose

Provide detail on data quality issues that we intend to raise with sites during routine data cycle. Contains both study specific data quality issues submitted within the last quarter or rolled over from prior data cycles in addition to issues flagged in network data quality assessment.


# NDQ: Checks without Thresholds

```{r}
find_no_threshold<-function(db=config('db_src'),
                            schema_name=config('results_schema')){
   tbl_names <-
    db %>%
    DBI::dbListObjects(DBI::Id(schema= schema_name)) %>%
    dplyr::pull(table) %>%
    purrr::map(~slot(.x, 'name')) %>%
    dplyr::bind_rows()%>%
    filter(str_detect(table, '^thr_'))%>%
     select(table)%>%pull()
     
     rslt<-tibble(check_name=NA_character_,
                  check_name_app=NA_character_)
     for(i in 1:length(tbl_names)){
       new_rslts<-results_tbl(tbl_names[i])%>%
         filter(is.na(threshold),site!='total')%>%
         distinct(check_name, check_name_app)%>%collect()
       if(all(is.na(rslt))){rslt<-new_rslts}else{rslt<-rslt%>%bind_rows(new_rslts)}
     }
     return(rslt)
}

no_threshold<-find_no_threshold(db=ndq_session$config('db_src'),
                             schema_name='dqa_rox')%>%
  left_join(metadata, by = 'check_name')

no_threshold_expected<-no_threshold%>%
  filter(str_detect(check_name,'vispc|viscn')|
           check_name%in%c('dcon_labsfluneg-condsflu',
                           'dcon_labsrsvneg-condsrsv'))
```

## No Threshold Expected

```{r nothreshexpect}
gt(no_threshold_expected%>%
     select(check_type, check_name, check_domain, check_application, full_description)%>%
     arrange(check_name))%>%
    tab_options(row_group.font.weight = 'bold',
              container.height='750px',
              container.overflow.y=TRUE)
```

## No Threshold - may want to assign

```{r}
gt(no_threshold%>%
     anti_join(no_threshold_expected, by = 'check_name')%>%
     select(check_type, check_name, check_domain, check_application, full_description)%>%
     arrange(check_name))%>%
    tab_options(row_group.font.weight = 'bold',
              container.height='750px',
              container.overflow.y=TRUE)
```

# SSDQA Issues

Issues raised in previous cycle + responses

```{r}
prev_ssdqa<-prev_session$results_tbl('dqa_issues_redcap')%>%
  filter(app=='ssdqa')%>%collect()%>%
  select(site, narrative, priority, status, fix_yn, violation_why, finalflag)
```

```{r}
gt(prev_ssdqa)%>%
  fmt_markdown(columns=c(narrative))%>%
  data_color(columns=c(site))%>%
  data_color(
  columns = priority,
  fn = function(x) coalesce(c("High"="#f7786f", "Medium"="#f7d36f", "Low"="#6fc973")[as.character(x)], "gray"))
```

New issues to be raised this cycle

```{r}
ssdqa_new<-results_tbl('ssdqa_issues_new')%>%
  select(site, narrative)%>%
  collect()

gt(ssdqa_new)%>%
  fmt_markdown(columns=c(narrative))%>%
  data_color(columns=c(site))
```


# All issues to be raised

* `new_issue` indicates whether this issue was raised in the previous data cycle (N) or not (Y)
* Symbols for each row indicate whether site has improved (`r fa("fas fa-arrow-up",fill="green")`), regressed (`r fa("fas fa-arrow-down",fill="red")`), or stayed the same compared with the prior cycle for recurrent issues.

```{r}
prev_issues<-prev_session$results_tbl('threshold_tbl_violations')%>%
  select(site, check_name_app, threshold, value_output)%>%
  rename(threshold_prev=threshold,
         value_prev=value_output)%>%
  collect()
new_issues<-viol%>%
  left_join(prev_issues, by = c('site','check_name_app'))%>%
  mutate(new_issue=case_when(is.na(value_prev)~"Y",
                             TRUE~"N"),
         better=case_when((new_issue=="N"&
                            (value_output==value_prev|abs(value_prev-value_output)<.005))~"circle",
                          (new_issue=="N"&
                             (threshold_operator=="lt"&value_output>value_prev)|
                             (threshold_operator=="gt"&value_output<value_prev))~"arrow-up",
                          (new_issue=="N"&
                             (threshold_operator=="lt"&value_output<value_prev)|
                             (threshold_operator=="gt"&value_output>value_prev))~"arrow-down",
                          new_issue=="Y"~"minus",
                          TRUE~"circle"))

gt(new_issues%>%
     select(site, check_type, check_name_app,threshold,threshold_operator,value_output,new_issue,value_prev, better)%>%
     arrange(site)%>%
     group_by(site))%>%
    tab_options(row_group.background.color = 'aliceblue',
              row_group.font.weight = 'bold',
              container.height='750px',
              container.width='1000px',
              container.overflow.y=TRUE)%>%
  fmt_number(decimals=2)%>%
  fmt_icon(columns=better,
           fill_color = c("arrow-up" = "green", "arrow-down" = "red", "circle" = "black", "minus"="black"))%>%
  data_color(
    columns = new_issue,
    fn = function(x) coalesce(c("Y"="#f7786f", "N"="#f7d36f")[as.character(x)], "gray"))%>%
  cols_label(
    check_type=md("**check_type**"),
    check_name_app=md("**check_name_app**"),
    threshold=md("**threshold**"),
    threshold_operator="",
    value_output=md("**value_output**"),
    new_issue=md("**new_issue**"),
    value_prev=md("**value_prev**"),
    better="")

```

